Paper 2, Econ 980x

### 2022-11-28 Paper2.Rmd
commit

@@

csv %>%
  group_by(year) %>%
  summarize(quantile(bls_leis, 0.25), quantile(bls_leis, 0.5), quantile(bls_leis, 0.75)) %>%
  clean_names() %>%
  pivot_longer(!year, names_to = "quantile", values_to = "hours") %>%
  filter(year > 2006) %>%
  filter(year < 2011) %>%
  ggplot(aes(x = year, y = hours, group = quantile)) +
  geom_line()

@@

stargazer(a, b, c, d, title="Various Models", align=TRUE, type = "text")
```

@@

@@

@@

@@

>>>>

# Median 
csv %>%
  filter(year > 2005) %>%
  filter(year < 2011) %>%
  group_by(year, gender) %>%
  summarize(median(bls_leis)) %>%
  clean_names() %>%
  ggplot(aes(x = year, y = median_bls_leis)) +
  geom_line() +
  facet_wrap(~ gender) +
  labs(
  title = "Median annual individual leisure hours by gender",
  y = "Annual Hours",
  x = "Year",
  caption = "Data from ATUS",
)

# Mean
csv %>%
  filter(year > 2005) %>%
  filter(year < 2011) %>%
  group_by(year, gender) %>%
  summarize(mean(bls_leis)) %>%
  clean_names() %>%
  ggplot(aes(x = year, y = mean_bls_leis)) +
  geom_line() +
  facet_wrap(~ gender) +
  labs(
  title = "Mean annual individual leisure hours by gender",
  y = "Annual Hours",
  x = "Year",
  caption = "Data from ATUS",
)

@@

csv %>%
  group_by(year) %>%
  summarize(quantile(bls_leis, 0.25), quantile(bls_leis, 0.5), quantile(bls_leis, 0.75)) %>%
  clean_names() %>%
  pivot_longer(!year, names_to = "quantile", values_to = "hours") %>%
  filter(year > 2005) %>%
  filter(year < 2011) %>%
  ggplot(aes(x = year, y = hours, group = quantile)) +
  geom_line()

@@

stargazer(a, b, c, d, title="Various Models", align=TRUE, type = "text")
```
```{r employment}

newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2011) %>%
  group_by(year) %>%
  count(emp) %>%
  filter(emp == "Unemployed") %>%
  ggplot(mapping = aes(x = year, y = n)) +
  geom_line() +
  labs(
  title = "Unemployment",
  y = "Annual Hours",
  x = "Count",
  caption = "Data from ATUS",
)
  #facet_wrap(~emp)

newcsv1 %>%
  ggplot(mapping = aes(x = bls_leis)) +
  geom_histogram() +
  facet_wrap(~emp)

newcsv1 %>%
  group_by(emp, gender, new_educ, year) %>%
  summarize(median = median(bls_leis)) %>%
  ggplot(mapping = aes(x = year, y = median, group = new_educ, colour = new_educ)) +
  geom_line() +
  facet_wrap(~gender + emp) +
  labs(
  title = "Annual individual leisure hours",
  y = "Annual Hours",
  x = "Count",
  caption = "Data from ATUS",
)

newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2011) %>%
  group_by(emp, gender, new_educ, year) %>%
  summarize(median = median(bls_leis)) %>%
  ggplot(mapping = aes(x = year, y = median, group = new_educ, colour = new_educ)) +
  geom_line() +
  facet_wrap(~gender + emp) +
  labs(
  title = "Annual individual leisure hours",
  y = "Annual Hours",
  x = "Count",
  caption = "Data from ATUS",
)

newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2011) %>%
  group_by(emp, gender) %>%
  tally()

```{r population_of_employment}

newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2011) %>%
  group_by(emp, year) %>%
  tally() %>%
  pivot_wider(names_from = year, values_from = n) %>%
  clean_names() %>%
  mutate(change_2008 = x2008-x2007) %>%
  mutate(change_2009 = x2009-x2008) %>%
  mutate(change_2010 = x2010-x2009) %>%
  select(1, 6:8)

@@

change11 <- newcsv1 %>%
  group_by(gender,  year, new_educ, child, marst_simple, emp) %>%
  summarize(median(bls_leis)) %>%
  clean_names() %>%
  pivot_wider(values_from = median_bls_leis, names_from = year) %>%
  clean_names() %>%
  mutate(leisure_change = x2009 - x2007)

@@

change12 <- newcsv1 %>%
  group_by(gender,  year, emp) %>%
  summarize(median(bls_leis)) %>%
  clean_names() %>%
  pivot_wider(values_from = median_bls_leis, names_from = year) %>%
  clean_names() %>%
  mutate(leisure_change = x2009 - x2007)

@@

delta11 <- change11 %>%
  lm(formula = leisure_change ~ gender+ new_educ+ child+ marst_simple + emp)
summary(delta11)

delta12 <- change12 %>%
  lm(formula = leisure_change ~ gender + emp)
summary(delta12)

@@

```{r}
